Vertical and oblique transmission with fluctuating transmission

### 2018-03-26 ms/fluctuating_oblique.tex
better figure for k=1

\paragraph{Period of one: $A1B1$.}
In the case of $k=1$ we can find $x^*$ the frequency of $A$ at the protected polymorphism.
Denote $F_B(F_A(x))-x = G(x) \cdot x (1-x) \cdot \gamma$ with
\begin{equation} \begin{aligned} \label{eq:xstar_periodic_fluc_k=1}
G(x) &= ax^2+bx+c, \\
\gamma &= -\frac{1 + sx}{s} \Big[ 1 + s + s^2 x (1-\rho)(1+x)\Big], \\
a &= s^2 \rho_A (1-\rho_A) (1 - \rho_B + \rho_B/\rho_A)) > 0, \\
b &= s(1-\rho_A)(2\rho_B - s\rho_A(1-\rho_B)), \\
c &= \rho_B - \rho_A - s\rho_A(1-\rho_B),
\end{aligned} \end{equation}
% $a+b+c>0$.
and then $x^*$ is a solution of the quadratic $G(x)=0$. %, given by $x^* = \frac{-b \pm \sqrt{b^2-4ac}}{2a}$.
The condition \eqref{eq:poly_condition_periodic_fluc}, which guarantees that $0 < x^* < 1$, is equivalent to $c<0$, and therefore it also guarantees that $\sqrt{b^2-4ac} > b$.
So, if $0<s<1$ (such that $b$ is guaranteed to be positive) then $x^*= \frac{-b+\sqrt{b^2-4ac}}{2a}$.
\autoref{fig:rho1_rho2_k=1} shows $x^*$, highlighting the area of the parameter space in which a protected polymorphism exists.

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=0.65\linewidth]{../figures/{rho1_rho2_k=1}.pdf}
\caption{
\textbf{Protected polymorphism with fluctuating transmission and selection.}
The positive root $x^*$ of $G(x)$, see~\eqref{eq:xstar_periodic_fluc_k=1}.
Dashed lines represent, from left to right, $\rho_B=\frac{\rho_A}{1+s(1-\rho_A)}$, $\rho_B=\rho_A$, and $\rho_B=\frac{(1+s)\rho_A}{1+s\rho_A}$, see~\eqref{eq:poly_condition_periodic_fluc}.
Here, $\rho_A=0.5$, $s=0.1$.}
\label{fig:rho1_rho2_k=1}
\end{figure*}

@@

% TODO plot \rho_B - \rho_A vs s and show the boundaries

@@

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.75\linewidth]{../figures/{rho1_rho2_stoch_p}.pdf}
\caption{
\textbf{Stochastic local stability.}
Here, $s_t=s$ and $\rho_t=\rho_1$ with probability $p=0.505$ and $s_t=-s$ and $\rho_t=\rho_2$ with probability $1-p=0.495$, with $s=0.05$ and $p=0.505$, a combination that allows a stochastic polymorphism with a fixed vertical transmission rate $\rho=0.1$ in~\citet[Fig.~2]{Ram2018}.}
\label{fig:rho1_rho2_stoch_p}
\end{figure*}

>>>>

\paragraph{Period of one: $A1B1$.}
In the case of $k=1$ we can find $x^*$ the frequency of $A$ at the protected polymorphism.
Denote $F_B(F_A(x))-x = G(x) \cdot x (1-x) \cdot \gamma$ with
\begin{equation} \begin{aligned} \label{eq:xstar_periodic_fluc_k=1}
G(x) &= ax^2+bx+c, \\
\gamma &= -\frac{1 + sx}{s} \Big[ 1 + s + s^2 x (1-\rho)(1+x)\Big], \\
a &= s^2 \rho_A (1-\rho_A) (1 - \rho_B + \rho_B/\rho_A)) > 0, \\
b &= s(1-\rho_A)(2\rho_B - s\rho_A(1-\rho_B)), \\
c &= \rho_B - \rho_A - s\rho_A(1-\rho_B),
\end{aligned} \end{equation}
% $a+b+c>0$.
and then $x^*$ is a solution of the quadratic $G(x)=0$. %, given by $x^* = \frac{-b \pm \sqrt{b^2-4ac}}{2a}$.
The condition \eqref{eq:poly_condition_periodic_fluc}, which guarantees that $0 < x^* < 1$, is equivalent to $c<0$, and therefore it also guarantees that $\sqrt{b^2-4ac} > b$.
So, if $0<s<1$ (such that $b$ is guaranteed to be positive) then $x^*= \frac{-b+\sqrt{b^2-4ac}}{2a}$.
\autoref{fig:rho1_rho2_phase_k=1} shows $x^*$, highlighting the area of the parameter space in which a protected polymorphism exists. The figure demonstrates that the stronger selection is (x-axis), the greater the fluctuations in $\rho$ can be (y-axis) while still maintaining a polymorphic population (area between the dashed lines).

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=0.65\linewidth]{../figures/{rho1_rho2_phase_k=1}.pdf}
\caption{
\textbf{Protected polymorphism.}
The stable equilibrium of the frequency of phenotype $A$ (\eqref{eq:xstar_periodic_fluc_k=1}) for different selection coefficients ($s$, x-axis) and difference between vertical transmission rates ($\rho_B-\rho_A$, y-axis) when both selection and transmission fluctuate every generation ($k=1$).
Dashed lines represent $\rho_B=\frac{\rho_A}{1+s(1-\rho_A)}$ and $\rho_B=\frac{(1+s)\rho_A}{1+s\rho_A}$, the limits on $\rho_B-\rho_A$ that allow a protected polymorphism (\eqref{eq:poly_condition_periodic_fluc}).
Here, $\rho_A=0.5$.}
\label{fig:rho1_rho2_phase_k=1}
\end{figure*}

@@

@@

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.75\linewidth]{../figures/{rho1_rho2_stoch_p}.pdf}
\caption{
\textbf{Stochastic local stability.}
Here, $s_t=0.05$ and $\rho_t=\rho_1$ with probability $p=0.505$ and $s_t=-0.05$ and $\rho_t=\rho_2$ with probability $1-p=0.495$, a combination that allows a stochastic polymorphism with a fixed vertical transmission rate $\rho=0.1$ in~\citet[Fig.~2]{Ram2018}.}
\label{fig:rho1_rho2_stoch_p}
\end{figure*}
